---
title: "Data_Mining"
author: "Bhavna Chouhan"
output: html_document
---
Install tidy packages 
```{r basicconsole}install.packages("tidyverse")
library(dplyr)
library(tidyr)
```

Load and examin the datset 
```{r basicconsole}cust.df <- read.csv("http://goo.gl/PmPkaG")
str(cust.df)
```

Find columns with missing values and zeros 
```{r basicconsole} colSums(is.na(cust.df))
any.na <- lapply(cust.df, function(x){length(which(x==0))}) 
any.na
```
Replace missing satisfaction service and selection values with mean
```{r basicconsole} cust.df$sat.service[is.na(cust.df$sat.service)] = round(mean(cust.df$sat.service)) 
 cust.df$sat.selection[is.na(cust.df$sat.selection)] = round(mean(cust.df$sat.selection))
table(cust.df$sat.selection)
table(cust.df$sat.service)
```
Turn email into a binary variable 

```{r basicconsole} table(cust.df$email)
cust.df<- cust.df %>% mutate(email = ifelse(email == "yes",1,0)) 
str(cust.df) 
```

Creat two new columns;'total.spend' that contains the sum of online and store spending for each customer and'total.trans'that contains the sum of online.trans and store.trans
```{r basicconsole} cust.df<- cust.df %>% mutate(total.spend = (online.spend + store.spend)) %>% 
mutate(total.trans = (online.trans+store.trans)) %>% 
mutate(total.spend = round(total.spend,1))
cust.df <- round(cust.df,0)
```

Divide the customers into four categories based on the total amount spent by them

```{r}levels<- c(-Inf,50,250,500,4000) 
labels <-c("Prospects","Regular","Premium","VIP")
cust.df <- cust.df %>% mutate(cust.category = cut(total.spend,levels,labels = labels))
str(cust.df)
max(cust.df$total.spend)
table(cust.df$cust.category)
``` 
Identify the customers as per their categories by selecting cust.id for each group 

```{r}
Target_Prospects <- cust.df[cust.df$cust.category == "Prospects","cust.id"] 
Target_Regular <- cust.df[cust.df$cust.category == "Regular", "cust.id"] 
Target_Premium <- cust.df[cust.df$cust.category == "Premium", "cust.id"]
Target_VIP <- cust.df[cust.df$cust.category == "VIP", "cust.id"]
Target_VVIP <- cust.df[cust.df$cust.category == "VVIP", "cust.id"]
```
Map the percentage of every customer category for distinct satisfaction ratings. 

```{r}
service_dist_Prospects <- cust.df[cust.df$cust.category == "Prospects", "sat.service"]
service_dist_Prospects
service_dist_Regular <- cust.df[cust.df$cust.category == "Regular","sat.service"]
service_dist_Regular
service_dist_Premium <- cust.df[cust.df$cust.category == "Premium","sat.service"]
service_dist_Premium
service_dist_VIP <- cust.df[cust.df$cust.category == "VIP","sat.service"]
service_dist_VIP
service_dist_VVIP <- cust.df[cust.df$cust.category == "VVIP","sat.service"]
service_dist_VVIP
```
Find percetage wise distribution for each category 
```{r}
prop.table(table(service_dist_Prospects))
prop.table(table(service_dist_Regular))
prop.table(table(service_dist_Premium))
prop.table(table(service_dist_VIP))
```

prop.table(table(service_dist_VVIP)) 
